Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-30 main.tex
fixed typsetting error
Added references to the caches diagram.

% CPU CACHE DISCUSSION
%2MB = 2**21 bytes
%64*64*4 = 2**14 bytes = 16384 bytes per image
%... so can fit 2**7  = 128 images.
Each core has a private 32\,KB L1 data cache and a private 256\,KB L2 cache.  
Between the 8 cores, this is a total of 2\,MB L2 cache.
For the low resolution images used in sparse representation based
face recognition (on the order of $64\times64$ pixel images), the L2 cache
can in principle hold up to 128 image vectors.
%16MB = 2**24 bytes = 16777216 bytes
%64*64*4 = 2**14 bytes = 16384 bytes per image
%... so can fit 2**10  = 1024 images.
Each processor further has 8MB of L3 cache that is shared by all four cores.
Overall, this means the algorithm has approximately 16MB of on-chip cache
available.  This corresponds to 1024 image vectors.

@@

% GPU CACHE DISCUSSION
% for L2 cache
% 768KB = 786432 bytes
% 64*64*4 = 2**14 bytes = 16384 bytes per image
% 48 images
Each SMP contains its own L1-cache, which is divided between hardware managed
and software managed ("shared") memory.  Additionally, all SMPs share a common
L2-cache.  For our system, each SMP has 64 KB of L1 cache with a total of 896
KB of L1 cache/shared memory and 768KB of L2 cache. The relatively small amount
of cache (1/23 as much as CPU L3) on the GPU is ballanced by a significantly
higher bandwidth between the processor chip and off-chip memory (DRAM) compared
to the CPU.

@@

The first experiment compares the performance of our two proposed implementations of 
the general $\ell_1$-minimization problem (Algorithm \eqref{alg:alm}) given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit column norm.  The ratio of $d:n$ varied from
$1:10$ to $5:10$ with $n$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ had a sparsity rate of 0.1 with elements generated using the standard normal and also normalized with unit norm.
Because the ground truth signal $\xx_0$ was known, the algorithm terminated
when $\|\bx-\bx_0\| < \tau$.
The measurement vector was generated with the equation $\b_0 = A \x_0$.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figures/caches}
\end{center}
\caption{Scale Drawing of the CPU and GPU cache sizes}
\label{fig:caches}
\end{figure}

% CPU CACHE DISCUSSION
%2MB = 2**21 bytes
%64*64*4 = 2**14 bytes = 16384 bytes per image
%... so can fit 2**7  = 128 images.
Each core has a private 32\,KB L1 data cache and a private 256\,KB L2 cache.  
Between the 8 cores, this is a total of 2\,MB L2 cache.
For the low resolution images used in sparse representation based
face recognition (on the order of $64\times64$ pixel images), the L2 cache
can in principle hold up to 128 image vectors.
%16MB = 2**24 bytes = 16777216 bytes
%64*64*4 = 2**14 bytes = 16384 bytes per image
%... so can fit 2**10  = 1024 images.
Each processor further has 8MB of L3 cache that is shared by all four cores.
Overall, this means the algorithm has approximately 16MB of on-chip cache
available.  This corresponds to 1024 image vectors.  A scale drawing
of the caches of the processor we're targeting can be seen in Figure \ref{fig:caches}.

@@

% GPU CACHE DISCUSSION
% for L2 cache
% 768KB = 786432 bytes
% 64*64*4 = 2**14 bytes = 16384 bytes per image
% 48 images
Each SMP contains its own L1-cache, which is divided between hardware managed
and software managed ("shared") memory.  Additionally, all SMPs share a common
L2-cache.  For our system, each SMP has 64 KB of L1 cache with a total of 896
KB of L1 cache/shared memory and 768KB of L2 cache. The relatively small amount
of cache (1/23 as much as CPU L3) on the GPU is balanced by a significantly
higher bandwidth between the processor chip and off-chip memory (DRAM) compared
to the CPU.  A scale drawing of the caches available on the GPU can be seen in Figure \ref{fig:caches}.

@@

The first experiment compares the performance of our two proposed implementations of 
the general $\ell_1$-minimization problem (Algorithm \eqref{alg:alm}) given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit column norm.  The ratio of $d:n$ varied from
$1:10$ to $5:10$ with $n$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ had a sparsity rate of 0.1 with elements generated using the standard normal and also normalized with unit norm.
Because the ground truth signal $\xx_0$ was known, the algorithm terminated
when $\|\bx-\bx_0\| < \tau$.
The measurement vector was generated with the equation $\bb_0 = A \xx_0$.
